---
title: "Assignment 4 - Coordinating Heart Rate"
author: "Dana Jensen"
date: "November 6, 2017"
output: html_document
---
---
                          "INCOMPLETE"
---

```{r setup, include=FALSE}
#preamble
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/Dana/Desktop/METHODS III/AssignmentVIII")
library(pacman)
p_load(ggplot2, caret, groupdata2, dplyr, tidyr, crqa, stringr, lmerTest, lme4, magrittr, cvms, gridExtra)
convo = read.csv("Study2_G7_T1_Conversation.csv")
sync = read.csv("Study2_G7_T2_Synchronous.csv")
turns = read.csv("Study2_G7_T3_TurnTaking.csv")

```
## Analysing Heart Rate and Respiration data
```{r}
### Step by step suggestions to solve the assignment

### Exploring physiological signals
# - Produce a plot of the participants' respiration signal and a different one of the participants' HR signal (for inspecting whether the data is usable)
#   N.B: remember the slides: artifacts, downsampling, scaling.
#   N.B. The gridExtra::grid.arrange() function allows you to display the plots side by side. E.g. grid.arrange(plot1, plot2, plot3, ncol=3)

#STEP ONE: REMOVING ARTIFACTS
removeOuts = function(ts,threshold){
  ts[ts> (mean(ts, na.rm=T)+
      (threshold*sd(ts,na.rm=T))) |
    ts < (mean(ts,na.rm=T) -
     (threshold*sd(ts,na.rm=T)))] = 
mean(ts, na.rm=T)
return(ts)}
threshold=2.5

#Condition 1
convo$HR1 = removeOuts(convo$HR1,threshold)
convo$HR2 = removeOuts(convo$HR2,threshold)
convo$Resp1 = removeOuts(convo$Resp1,threshold)
convo$Resp2 = removeOuts(convo$Resp2,threshold)

#Condition 2
sync$HR1 = removeOuts(sync$HR1,threshold)
sync$HR2 = removeOuts(sync$HR2,threshold)
sync$Resp1 = removeOuts(sync$Resp1,threshold)
sync$Resp2 = removeOuts(sync$Resp2,threshold)

#Condtition 3
turns$HR1 = removeOuts(turns$HR1,threshold)
turns$HR2 = removeOuts(turns$HR2,threshold)
turns$Resp1 = removeOuts(turns$Resp1,threshold)
turns$Resp2 = removeOuts(turns$Resp2,threshold)

#STEP TWO: SCALING

#Condition 1
convo$Resp1 = scale(convo$Resp1)
convo$Resp2 = scale(convo$Resp2)
convo$HR1 = scale(convo$HR1)
convo$HR2 = scale(convo$HR2)

#Condition 2
sync$Resp1 = scale(sync$Resp1)
sync$Resp2 = scale(sync$Resp2)
sync$HR1 = scale(sync$HR1)
sync$HR2 = scale(sync$HR2)

#Condition 3
turns$Resp1 = scale(turns$Resp1)
turns$Resp2 = scale(turns$Resp2)
turns$HR1 = scale(turns$HR1)
turns$HR2 = scale(turns$HR2)

#STEP THREE: DOWN-SAMPLING

#Condition 1
convo1 = convo%>%
  group(n=100,method='greedy')%>% 
  dplyr::summarise(time=mean(time[!is.na(time) & !is.nan(time) & !is.infinite(time)]),HR1=mean(HR1[!is.na(HR1) & !is.nan(HR1) & !is.infinite(HR1)]),HR2=mean(HR2[!is.na(HR2) & !is.nan(HR2) & !is.infinite(HR2)]),RESP1=mean(Resp1[!is.na(Resp1) & !is.nan(Resp1) & !is.infinite(Resp1)]),RESP2=mean(Resp2[!is.na(Resp2) & !is.nan(Resp2) & !is.infinite(Resp2)]))

#Condition 2
sync1 = sync%>%
  group(n=100,method='greedy')%>% 
  dplyr::summarise(time=mean(time[!is.na(time) & !is.nan(time) & !is.infinite(time)]),HR1=mean(HR1[!is.na(HR1) & !is.nan(HR1) & !is.infinite(HR1)]),HR2=mean(HR2[!is.na(HR2) & !is.nan(HR2) & !is.infinite(HR2)]),RESP1=mean(Resp1[!is.na(Resp1) & !is.nan(Resp1) & !is.infinite(Resp1)]),RESP2=mean(Resp2[!is.na(Resp2) & !is.nan(Resp2) & !is.infinite(Resp2)]))

#Condition 3
turns1 = turns%>%
  group(n=100,method='greedy')%>% 
  dplyr::summarise(time=mean(time[!is.na(time) & !is.nan(time) & !is.infinite(time)]),HR1=mean(HR1[!is.na(HR1) & !is.nan(HR1) & !is.infinite(HR1)]),HR2=mean(HR2[!is.na(HR2) & !is.nan(HR2) & !is.infinite(HR2)]),RESP1=mean(Resp1[!is.na(Resp1) & !is.nan(Resp1) & !is.infinite(Resp1)]),RESP2=mean(Resp2[!is.na(Resp2) & !is.nan(Resp2) & !is.infinite(Resp2)]))

#STEP FOUR: PLOTTING
#(I'm sorry you have to see this *embarrassed emoji*)

#Condition 1
H1H2_1<-ggplot(convo1, aes(time, HR1))+
  geom_line()+
  geom_line(aes(time, HR2), color = 'Red')+
  labs(title ="Condition1 HR 1&2", x = "Time", y = "HR")
R1R2_1<-ggplot(convo1, aes(time, RESP1))+
  geom_line()+
  geom_line(aes(time, RESP2), color = 'Red')+
  labs(title ="Condition1 RESP 1&2", x = "Time", y = "RESP")
H1R2_1<-ggplot(convo1, aes(time, HR1))+
  geom_line()+
  geom_line(aes(time, RESP2), color = 'Red')+
  labs(title ="Condition1 HR1 & RESP2", x = "Time", y = "Scaled HR & RESP")
H2R1_1<-ggplot(convo1, aes(time, HR2))+
  geom_line()+
  geom_line(aes(time, RESP1), color = 'Red')+
  labs(title ="Condition1 HR2 & RESP1", x = "Time", y = "Scaled HR & RESP")

#Condition 2
H1H2_2<-ggplot(sync1, aes(time, HR1))+
  geom_line()+
  geom_line(aes(time, HR2), color = 'Red')+
  labs(title ="Condition2 HR 1&2", x = "Time", y = "HR")
R1R2_2<-ggplot(sync1, aes(time, RESP1))+
  geom_line()+
  geom_line(aes(time, RESP2), color = 'Red')+
  labs(title ="Condition2 RESP 1&2", x = "Time", y = "RESP")
H1R2_2<-ggplot(sync1, aes(time, HR1))+
  geom_line()+
  geom_line(aes(time, RESP2), color = 'Red')+
  labs(title ="Condition2 HR1 & RESP2", x = "Time", y = "Scaled HR & RESP")
H2R1_2<-ggplot(sync1, aes(time, HR2))+
  geom_line()+
  geom_line(aes(time, RESP1), color = 'Red')+
  labs(title ="Condition2 HR2 & RESP1", x = "Time", y = "Scaled HR & RESP")

#Condition 3
H1H2_3<-ggplot(turns1, aes(time, HR1))+
  geom_line()+
  geom_line(aes(time, HR2), color = 'Red')+
  labs(title ="Condition3 HR 1&2", x = "Time", y = "HR")
R1R2_3<-ggplot(turns1, aes(time, RESP1))+
  geom_line()+
  geom_line(aes(time, RESP2), color = 'Red')+
  labs(title ="Condition3 RESP 1&2", x = "Time", y = "RESP")
H1R2_3<-ggplot(turns1, aes(time, HR1))+
  geom_line()+
  geom_line(aes(time, RESP2), color = 'Red')+
  labs(title ="Condition3 HR1 & RESP2", x = "Time", y = "Scaled HR & RESP")
H2R1_3<-ggplot(turns1, aes(time, HR2))+
  geom_line()+
  geom_line(aes(time, RESP1), color = 'Red')+
  labs(title ="Condition3 HR2 & RESP1", x = "Time", y = "Scaled HR & RESP")


H1H2<-grid.arrange(H1H2_1,H1H2_2,H1H2_3, ncol = 3)
R1R2<-grid.arrange(R1R2_1,R1R2_2,R1R2_3, ncol = 3)
HR<-grid.arrange(H1R2_1,H1R2_2,H1R2_3,H2R1_1,H2R1_2,H2R1_3, ncol = 3)
# - Can you eye-ball which condition if any displays more physiological coordination?
```

```{r}
# - Run crqa on heart rate and respiration data (find parameters, run crqa)

#okay, now back to business
par = list(lgM =  10, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = 'mindip')

#FINDING OPTIMIZED PARAMETERS
# I am seriously so sorry for what is about to happen....

#######CONDITION 1#######

###Heart Rate 1&2

#optimizing parameters
try(optimizeParam(convo1$HR1, convo1$HR2, par, min.rec = 1, max.rec = 10))
#delay = 0(porque?), embed = 20, radius = 0.69

#crqa
HR1<-crqa(convo1$HR1, convo1$HR2, embed = 20, delay = 1, normalize = 0, rescale = 0, radius = 0.69, mindiagline = 2, minvertline = 1)

#Making Plot
RP1=HR1$RP 
RP_1 = matrix(as.numeric(RP1), nrow = ncol(RP1))  
cols = c("white","black") 
image(RP_1, xlab = "HR1", ylab = "HR2", col = cols) 

#------------------------------------------------------------
###Respiration 1

#optimizing parameters
try(optimizeParam(convo1$RESP1, convo1$RESP2, par, min.rec = 1, max.rec = 10))
#delay = 4, embed = 2, radius = 0.35

#crqa
R1<-crqa(convo1$RESP1, convo1$RESP2, embed = 2, delay = 4, normalize = 0, rescale = 0, radius = .35, mindiagline = 2, minvertline = 1)

#Making Plot
RP2<-R1$RP 
RP_2 = matrix(as.numeric(RP2), nrow = ncol(RP2)) 
cols = c("white","black") 
image(RP_2, xlab = "RESP1", ylab = "RESP2", col = cols) 
#------------------------------------------------------------

###Heart rate 1 and Respiration 2

#optimizing parameters
try(optimizeParam(convo1$HR1,convo1$RESP2, par, min.rec = 1, max.rec = 10))
#delay = 5, embed = 20, radius = 2.42

#crqa
HRR1<-crqa(convo1$HR1, convo1$RESP2, embed = 20, delay = 5, normalize = 0, rescale = 0, radius = 2.42, mindiagline = 2, minvertline = 1)

#Making Plot
RP3=HRR1$RP 
RP_3 = matrix(as.numeric(RP3), nrow = ncol(RP3)) 
cols = c("white","black") 
image(RP_3, xlab = "HR1", ylab = "RESP2", col = cols) 
#------------------------------------------------------------
###Heart Rate 2 & Respiration 1

#optimizing parameters
try(optimizeParam(convo1$HR2, convo1$RESP2, par, min.rec = 1, max.rec = 10))
#delay = 0, embed = 8, radius = 0.36

#crqa
HRR2<-crqa(convo1$HR2, convo1$RESP2, embed = 8, delay = 1, normalize = 0, rescale = 0, radius = 0.36,mindiagline = 2, minvertline = 1)

#Making plot
RP4=HRR2$RP 
RP_4 = matrix(as.numeric(RP4), nrow = ncol(RP4)) 
cols = c("white","black") 
image(RP_1, xlab = "HR2", ylab = "Resp1", col = cols) 
 
#######CONDITION 2#######

###Heart Rate 1&2

#optimizing parameters
try(optimizeParam(sync1$HR1, sync1$HR2, par, min.rec = 1, max.rec = 10))
#delay = 8, embed = 20, radius = 2.31

#crqa
HR1<-crqa(sync1$HR1, sync1$HR2, embed = 20, delay = 8, normalize = 0, rescale = 0, radius = 2.31, mindiagline = 2, minvertline = 1)

#Making Plot
RP1=HR1$RP 
RP_1 = matrix(as.numeric(RP1), nrow = ncol(RP1))  
cols = c("white","black") 
image(RP_1, xlab = "HR1", ylab = "HR2", col = cols) 

#------------------------------------------------------------
###Respiration 1

#optimizing parameters
try(optimizeParam(sync1$RESP1, sync1$RESP2, par, min.rec = 1, max.rec = 10))
#delay = 9, embed = 16, radius = 2.79

#crqa
R1<-crqa(sync1$RESP1, sync1$RESP2, embed = 16, delay = 9, normalize = 0, rescale = 0, radius = 2.79, mindiagline = 2, minvertline = 1)

#Making Plot
RP2<-R1$RP 
RP_2 = matrix(as.numeric(RP2), nrow = ncol(RP2)) 
cols = c("white","black") 
image(RP_2, xlab = "RESP1", ylab = "RESP2", col = cols) 
#------------------------------------------------------------

###Heart rate 1 and Respiration 2

#optimizing parameters
try(optimizeParam(sync1$HR1,sync1$RESP2, par, min.rec = 1, max.rec = 10))
#delay = 9, embed = 16, radius = 2.79

#crqa
HRR1<-crqa(sync1$HR1, sync1$RESP2, embed = 16, delay = 9, normalize = 0, rescale = 0, radius = 2.79, mindiagline = 2, minvertline = 1)

#Making Plot
RP3=HRR1$RP 
RP_3 = matrix(as.numeric(RP3), nrow = ncol(RP3)) 
cols = c("white","black") 
image(RP_3, xlab = "HR1", ylab = "RESP2", col = cols) 
#------------------------------------------------------------
###Heart Rate 2 & Respiration 1

#optimizing parameters
try(optimizeParam(sync1$HR2, sync1$RESP1, par, min.rec = 1, max.rec = 10))
#delay = 0, embed = 7, radius = 0.36

#crqa
HRR2<-crqa(sync1$HR2, sync1$RESP1, embed = 7, delay = 1, normalize = 0, rescale = 0, radius = 0.36,mindiagline = 2, minvertline = 1)

#Making plot
RP4=HRR2$RP 
RP_4 = matrix(as.numeric(RP4), nrow = ncol(RP4)) 
cols = c("white","black") 
image(RP_4, xlab = "HR2", ylab = "Resp1", col = cols) 

#######CONDITION 3#######

###Heart Rate 1&2

#optimizing parameters
try(optimizeParam(turns1$HR1, turns1$HR2, par, min.rec = 1, max.rec = 10))
#delay = 8, embed = 20, radius = 2.31

#crqa
HR1<-crqa(turns1$HR1, turns1$HR2, embed = 20, delay = 8, normalize = 0, rescale = 0, radius = 2.31, mindiagline = 2, minvertline = 1)

#Making Plot
RP1=HR1$RP 
RP_1 = matrix(as.numeric(RP1), nrow = ncol(RP1))  
cols = c("white","black") 
image(RP_1, xlab = "HR1", ylab = "HR2", col = cols) 

#------------------------------------------------------------
###Respiration 1

#optimizing parameters
try(optimizeParam(turns1$RESP1, turns1$RESP2, par, min.rec = 1, max.rec = 10))
#delay = 9, embed = 16, radius = 2.79

#crqa
R1<-crqa(turns1$RESP1, turns1$RESP2, embed = 16, delay = 9, normalize = 0, rescale = 0, radius = 2.79, mindiagline = 2, minvertline = 1)

#Making Plot
RP2<-R1$RP 
RP_2 = matrix(as.numeric(RP2), nrow = ncol(RP2)) 
cols = c("white","black") 
image(RP_2, xlab = "RESP1", ylab = "RESP2", col = cols) 
#------------------------------------------------------------

###Heart rate 1 and Respiration 2

#optimizing parameters
try(optimizeParam(turns1$HR1,turns1$RESP2, par, min.rec = 1, max.rec = 10))
#delay = 9, embed = 16, radius = 2.79

#crqa
HRR1<-crqa(turns1$HR1, turns1$RESP2, embed = 16, delay = 9, normalize = 0, rescale = 0, radius = 2.79, mindiagline = 2, minvertline = 1)

#Making Plot
RP3=HRR1$RP 
RP_3 = matrix(as.numeric(RP3), nrow = ncol(RP3)) 
cols = c("white","black") 
image(RP_3, xlab = "HR1", ylab = "RESP2", col = cols) 
#------------------------------------------------------------
###Heart Rate 2 & Respiration 1

#optimizing parameters
try(optimizeParam(turns1$HR2, turns1$RESP1, par, min.rec = 1, max.rec = 10))
#delay = 0, embed = 7, radius = 0.36

#crqa
HRR2<-crqa(turns1$HR2, turns1$RESP1, embed = 7, delay = 1, normalize = 0, rescale = 0, radius = 0.36,mindiagline = 2, minvertline = 1)

#Making plot
RP4=HRR2$RP 
RP_4 = matrix(as.numeric(RP4), nrow = ncol(RP4)) 
cols = c("white","black") 
image(RP_4, xlab = "HR2", ylab = "Resp1", col = cols) 
#and this is the point which my computer could no longer take the abuse...
# - Does this tell you more than just eyeballing the plots?
```

```{r}
### Systematically pre-process the data
# - Loop through all the files (either with a loop or with a function), check which files should be excluded, if any, and save the pre-processed time-series. Tip: plot and visually inspect the data to figure out which should be excluded.

#rm(result_df)
path<-("C:/Users/Dana/Desktop/METHODS III/AssignmentVIII/data")
folder = file.path(path)
file_list<- list.files(path = folder, recursive = TRUE, pattern = "*.csv")
study = NULL
group = NULL
condition = NULL
HR1 = NULL
HR2 = NULL
RESP1 = NULL
RESP2 = NULL
time = NULL
name = NULL
temp= data.frame(HR1, HR2, RESP1, RESP2, time)
result_df = data.frame()
n = 1

#loop to pre-process data

#ONLY NEED TO DO THIS ONCE
for (file in file_list){
  i = read.csv(file)
  #downsample
  i1 = i%>%
    group(n=100,method='greedy')%>%
    dplyr::summarise(time=mean(time, na.rm=T),HR1=mean(HR1, na.rm = T),HR2=mean(HR2, na.rm = T),RESP1=mean(Resp1, na.rm = T),RESP2=mean(Resp2, na.rm = T))
  #removing outliers
  threshold=2.5
  HR1 = removeOuts(i1$HR1,threshold)
  HR2 = removeOuts(i1$HR2,threshold)
  RESP1 = removeOuts(i1$RESP1,threshold)
  RESP2 = removeOuts(i1$RESP2,threshold)
  #scaling
  RESP1 = scale(i1$RESP1)
  RESP2 = scale(i1$RESP2)
  HR1 = scale(i1$HR1)
  HR2 = scale(i1$HR2)
  time = i1$time
  #info
  group = rep(str_extract(str_extract(str_extract(file, "S\\w{4}\\d[:punct:]G\\d+"), "G\\d+"), "\\d+"), length(i1$time))
  condition['n'] = rep(str_extract(str_extract(str_extract(file, "S\\w{4}\\d+[:punct:]G\\d+[:punct:]T\\d+"), "T\\d+"), "\\d+"), length(i1$time))
  study['n'] = rep(str_extract(str_extract(str_extract(file, "S\\w{4}\\d+[:punct:]G\\d+[:punct:]T\\d+"), "S\\w{4}\\d+"), "\\d+"), length(i1$time))
  name = paste(file)
  temp = data.frame(time , HR1, HR2, RESP1, RESP2, name, study, group, condition)
  write.csv(temp, paste('clean', name, 'csv', sep = '.'))
  # 
  # if (n == 1){
  #    result_df = temp}
  #  else{
  #    result_df = rbind(result_df, temp)}
  # 
  n = n+1
}

time = NULL
HR1 = NULL
HR2 = NULL
RESP1 = NULL
RESP2 = NULL

make_effing_plots= function(file){
  i = read.csv(file)
  name = paste(file)
  temp = data.frame(time = i$time, HR1 = i$HR1, HR2 = i$HR2, RESP1 = i$RESP1, RESP2 = i$RESP2)
  plot_p1 = ggplot(temp, aes(x = time, y = HR1)) + 
    geom_line(color = "red") +   
    geom_line(aes(x = time, y = HR2), color = "green")
  plot_p2 = ggplot(temp, aes(x = time, y = RESP1)) + 
    geom_line(color = "red") +   
    geom_line(aes(x = time, y = RESP2), color = "green")
  megaplot<-grid.arrange(plot_p1, plot_p2) 
  return(megaplot)
}

path<-("C:/Users/Dana/Desktop/METHODS III/AssignmentVIII")
folder = file.path(path)
file_list<- list.files(path = folder, recursive = TRUE, pattern = "*.csv")

#I am sooooooo satisfied with myself right now
make_effing_plots(file = file_list[1])#no for resp
make_effing_plots(file = file_list[2])#no
make_effing_plots(file = file_list[3])#ok
make_effing_plots(file = file_list[4])#no for resp
make_effing_plots(file = file_list[5])#no for resp
make_effing_plots(file = file_list[6])#ok
make_effing_plots(file = file_list[7])#ok
make_effing_plots(file = file_list[8])#ok
make_effing_plots(file = file_list[9])#ok
make_effing_plots(file = file_list[10])#ok
make_effing_plots(file = file_list[11])#ok
make_effing_plots(file = file_list[12])#ok
make_effing_plots(file = file_list[13])#ok
make_effing_plots(file = file_list[14])#ok
make_effing_plots(file = file_list[15])#ok
make_effing_plots(file = file_list[16])#no for hr
make_effing_plots(file = file_list[17])#no for hr
make_effing_plots(file = file_list[18])#ok
make_effing_plots(file = file_list[19])#ok
make_effing_plots(file = file_list[20])#ok
make_effing_plots(file = file_list[21])#no for hr
make_effing_plots(file = file_list[22])#ok
make_effing_plots(file = file_list[23])#ok
make_effing_plots(file = file_list[24])#ok
make_effing_plots(file = file_list[25])#ok
make_effing_plots(file = file_list[26])#ok
make_effing_plots(file = file_list[27])#ok
make_effing_plots(file = file_list[28])#no for hr
make_effing_plots(file = file_list[29])#ok
make_effing_plots(file = file_list[30])#ok


names<-unlist(unique(file_list))#picks up old unprocessed data
names<-names[1:30]#we only want clean data
names<-names[3:30]#remove unwanted rebel scum from galactic republic

#try to make new df with only good data

#-I really want to make this work, but running out of time so I have to do it manually. So much easier to do in python. -.-

# file_list<- list.files(path = folder, recursive = TRUE, pattern = "*.csv")
# file_list<- file_list[1:30]
# n = 1
# i = file_list[1]
# for (x in length(names)){#28
#   if (name %in% names ==  file %in% file_list){#if name is same as file
#     i = read.csv(file)#only read files we want
#     temp = data.frame(time = i$time, HR1 = i$HR1, HR2 = i$HR2, RESP1 = i$RESP1, RESP2 = i$RESP2)#make df
#      if (n == 1){
#        result_df = temp
#     }else{
#        result_df = rbind(result_df, temp)}
#   n = n+1
# }}

S1G1T3<- read.csv("clean.Study1_G1_T3_SelfPaced.csv.csv")
S1G2T3<- read.csv("clean.Study1_G2_T3_SelfPaced.csv.csv")
S1G3T1<- read.csv("clean.Study1_G3_T1_SelfPaced.csv.csv")
S1G3T2<- read.csv("clean.Study1_G3_T2_TurnTaking.csv.csv") 
S1G3T3<- read.csv("clean.Study1_G3_T3_Synchronous.csv.csv")
S1G4T1<- read.csv("clean.Study1_G4_T1_Synchronous.csv.csv")
S1G4T2<- read.csv("clean.Study1_G4_T2_SelfPaced.csv.csv")
S1G4T3<- read.csv("clean.Study1_G4_T3_TurnTaking.csv.csv")
S2G10T1<- read.csv("clean.Study2_G10_T1_Conversation.csv.csv")
S2G10T2<- read.csv("clean.Study2_G10_T2_TurnTaking.csv.csv") 
S2G10T3<- read.csv("clean.Study2_G10_T3_Synchronous.csv.csv")
S2G5T1<- read.csv("clean.Study2_G5_T1_Synchronous.csv.csv")
S2G5T2<- read.csv("clean.Study2_G5_T2_TurnTaking.csv.csv") 
S2G5T3<- read.csv("clean.Study2_G5_T3_Conversation.csv.csv")
S2G6T1<- read.csv("clean.Study2_G6_T1_TurnTaking.csv.csv")
S2G6T2<- read.csv("clean.Study2_G6_T2_Conversation.csv.csv")
S2G7T1<- read.csv("clean.Study2_G7_T1_Conversation.csv.csv")
S2G7T2<- read.csv("clean.Study2_G7_T2_Synchronous.csv.csv")
S2G7T3<- read.csv("clean.Study2_G7_T3_TurnTaking.csv.csv")
S2G8T1<- read.csv("clean.Study2_G8_T1_TurnTaking.csv.csv")
S2G8T2<- read.csv("clean.Study2_G8_T2_Synchronous.csv.csv")
S2G8T3<- read.csv("clean.Study2_G8_T3_Conversation.csv.csv")
S2G9T2<- read.csv("clean.Study2_G9_T2_Conversation.csv.csv")
S2G9T3<-  read.csv("clean.Study2_G9_T3_TurnTaking.csv.csv")

#oh geeze...
good<- list(S1G1T3,S1G2T3,S1G3T1,S1G3T2,S1G3T3,S1G4T1,S1G4T2,S1G4T3,S2G10T1,S2G10T2,S2G10T3,S2G5T1,S2G5T2,S2G5T3,S2G6T1,S2G6T2,S2G7T1,S2G7T2,S2G7T3,S2G8T1,S2G8T2,S2G8T3,S2G9T2,S2G9T3)

# bad<-list(
# S1G2T1<- read.csv("clean.Study1_G2_T1_TurnTaking.csv.csv"),#(hr) 2
# S1G2T2<-read.csv("clean.Study1_G2_T2_Synchronous.csv.csv"),#(hr) 3
# S2G6T3<- read.csv("clean.Study2_G6_T3_Synchronous.csv.csv"),#(resp) 19
# S2G9T1<- read.csv("clean.Study2_G9_T1_Synchronous.csv.csv")#(resp) 26
# )
```

```{r}
# - Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.

#this is one hell of a function...
OP = function(dataset, x){ 
  par = list(lgM =  10, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip")
  opt_param = NULL
#condition 1: heart rate
  if (x == "1"){
    t1 = dplyr::select(dataset, HR1 )
    t2 = dplyr::select(dataset, HR2 )
    opt_param = try(optimizeParam(t1, t2, par, min.rec = 1, max.rec = 10))
      if (length(opt_param) > 1) {
        radius = opt_param[1]
        embed = opt_param[2]
        delay = opt_param[3]
      }else{
        radius = NA
        embed = NA
        delay = NA
      }
    result = c(radius, embed, delay)
#Condition 2: respiration    
    }else if (x == "2"){
      t1 = dplyr::select(dataset, RESP1 )
      t2 = dplyr::select(dataset, RESP2 )
      opt_param = try(optimizeParam(t1, t2, par, min.rec = 1, max.rec = 10))
      if (length(opt_param) > 1) {
        radius = opt_param[1]
        embed = opt_param[2]
        delay = opt_param[3]
      }else{
        radius = NA
        embed = NA
        delay = NA
      }
      result = c(radius, embed, delay)
      }
return(result)
}

#just a test to make sure it works
OP(dataset = S1G1T3, x = 2)
df<-data.frame((OP(dataset = S1G2T3, x = 1)))


##Can't get this one to work either so I have to do it manually :(
#all I want is to go through every dataframe in 'good' and get the optimized parameters, is that too much to ask?
# for (i in good){
#   for (y in seq(2)){
#     temp<-data.frame(OP(dataset = i, x = y))
#     type<- NULL
#     if(y == "1"){
#       type<- "HR"
#       temp$type<-type
#       df<-temp
#     }else if(y == "2"){
#       type<-"RESP"
#       temp$type<-type
#       df<-rbind(temp,df)
#     }
# }}

#jesus christ...
df<-data.frame((OP(dataset = S1G1T3, x = 1)),file = "S1G1T3", type="HR" )
df<- rbind(df, data.frame((OP(dataset = S1G1T3, x = 2)),file = "S1G1T3", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S1G2T3, x = 1)),file = "S1G2T3", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S1G2T3, x = 2)),file = "S1G2T3", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S1G3T1, x = 1)),file = "S1G3T1", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S1G3T1, x = 2)),file = "S1G3T1", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S1G3T2, x = 1)),file = "S1G3T2", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S1G3T2, x = 2)),file = "S1G3T2", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S1G3T3, x = 1)),file = "S1G3T3", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S1G3T3, x = 2)),file = "S1G3T3", type="RESP"))#bitch
df<- rbind(df, data.frame((OP(dataset = S1G4T1, x = 1)),file = "S1G4T1", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S1G4T1, x = 2)),file = "S1G4T1", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S1G4T2, x = 1)),file = "S1G4T2", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S1G4T2, x = 2)),file = "S1G4T2", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S1G4T3, x = 1)),file = "S1G4T3", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S1G4T3, x = 2)),file = "S1G4T3", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G5T1, x = 1)),file = "S2G5T1", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G5T1, x = 2)),file = "S2G5T1", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G5T2, x = 1)),file = "S2G5T2", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G5T2, x = 2)),file = "S2G5T2", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G5T3, x = 1)),file = "S2G5T3", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G5T3, x = 2)),file = "S2G5T3", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G6T1, x = 1)),file = "S2G6T1", type="HR"))#bitch
df<- rbind(df, data.frame((OP(dataset = S2G6T1, x = 2)),file = "S2G6T1", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G6T2, x = 1)),file = "S2G6T2", type="HR"))#bitch
df<- rbind(df, data.frame((OP(dataset = S2G6T2, x = 2)),file = "S2G6T2", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G7T1, x = 1)),file = "S2G7T1", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G7T1, x = 2)),file = "S2G7T1", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G7T2, x = 1)),file = "S2G7T2", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G7T2, x = 2)),file = "S2G7T2", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G7T3, x = 1)),file = "S2G7T3", type="HR"))#oh c'mon
df<- rbind(df, data.frame((OP(dataset = S2G7T3, x = 2)),file = "S2G7T3", type="RESP"))#you too
df<- rbind(df, data.frame((OP(dataset = S2G8T1, x = 1)),file = "S2G8T1", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G8T1, x = 2)),file = "S2G8T1", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G8T2, x = 1)),file = "S2G8T2", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G8T2, x = 2)),file = "S2G8T2", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G8T3, x = 1)),file = "S2G8T3", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G8T3, x = 2)),file = "S2G8T3", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G9T2, x = 1)),file = "S2G9T2", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G9T2, x = 2)),file = "S2G9T2", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G9T3, x = 1)),file = "S2G9T3", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G9T3, x = 2)),file = "S2G9T3", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G10T1, x = 1)),file = "S2G10T1", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G10T1, x = 2)),file = "S2G10T1", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G10T2, x = 1)),file = "S2G10T2", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G10T2, x = 2)),file = "S2G10T2", type="RESP"))
df<- rbind(df, data.frame((OP(dataset = S2G10T3, x = 1)),file = "S2G10T3", type="HR"))
df<- rbind(df, data.frame((OP(dataset = S2G10T3, x = 2)),file = "S2G10T3", type="RESP"))
           
#rethinking my life
















#then take median of op
```

```{r}


### Creating controls: shuffled controls
#  - loop through all pairs and conditions
#  - shuffle the timeseries (take a timeseries and rearrange its values in a random order). Tip check the sample() function

HR1<- NULL
HR2<- NULL
RESP1<- NULL
RESP2<- NULL

for (i in good){
  time<-i[[1]][[2]]
  HR1<-sample(i[[1]][[3]])
  HR2<-sample(i[[1]][[4]])
  RESP1<-sample(i[[1]][[5]])
  RESP2<-sample(i[[1]][[6]])
  new<- data.frame(time, HR1, HR2, RESP1, RESP2)
  assign(paste("new",i ,sep = "_"), new)
  }

#  - run crqa and save the output. NB. which delay, embed, radius parameters should you use?
dana_crqa<-function(dataframe, condition){
  if (condition =="1"){
  result<-crqa(dataframe$HR1, dataframe$HR2, embed = 7, delay = 1, normalize = 0, rescale = 0, radius = 0.36,mindiagline = 2, minvertline = 1)
  }else if(condition =="2"){
  result<-crqa(dataframe$RESP1, dataframe$RESP2, embed = 7, delay = 1, normalize = 0, rescale = 0, radius = 0.36,mindiagline = 2, minvertline = 1)  
  }
  RR[n]<- result$RR
  DET[n]<- result$DET
  maxL[n]<- result$maxL
  L[n]<- result$L
  TT[n]<- result$TT
  NRLINE[n]<- result$NRLINE
  crqa_df<- data.frame(RR, DET, maxL, L, TT, NRLINE)
  name <- comment(dataframe) 
  assign(paste("crqa",name,condition, sep = "_"), crqa_df)}
  return(crqa_df)
}
#  - statistically compare the crqa indexes in real and shuffled pairs
lmer(RR ~ pairing + condition + (1 | group) 

### TRICKY! Creating controls: surrogate pair controls

#  - Per each real pair, identify at least one surrogate pair (matching one of the participants, with somebody doing the same task, but in a different pair). Tip: Celine will share a commented script


#  - Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?


#  - Test whether crqa shows a difference between real and surrogate pairs

### Testing effects of conditions

#  - make a (probably underpowered) mixed model testing effects of the different conditions on heart rate and respiration coordination
#  - N.B: would it make sense to include surrogate pairs? and if so how? what would that tell you?


### Effects of respiration coordination on heart rate coordination

#  - describe how you would test those.

```

# 1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.
# 2) Do you observe interpersonal coordination in heart rate and respiration? Describe your control baseline, the method used to quantify coordination, and the statistical models used to infer whether coordination was higher than in the baseline. Report the results of the models.
# 3) Do you observe differences in coordination between conditions? Report the models and results.
# 4) Is respiration coordination a likely driver of heart rate coordination? Describe how you would test for it. Bonus points if you actually run the tests and report methods and results.
# 
# N.B. to give you a bit more data I included data from last year (Study1) and from your class (Study2). Note that synchronouns and turn-taking are the same across both studies, but the third condition is different: last year it was self-paced joint reading; this year it was the tv-series conversation. So you might want to exclude the self-paced reading (but, up to you!)